### 2020-02-10 submission/introduction.tex
fixed more typos

To answer this question, we analyze hundreds of publicly-available pretrained state-of-the-art CV and NLP models. 
Here is a summary of our main results.
\begin{itemize}
\item
Norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models.
%, i.e., they can be used to discriminate between ``good-better-best'' models.
\item
However, norm-based meterics may fail for poorly-trained well-trained, i.e., to distinguish ``good-versus-bad''~models.
\item 
PL-based metrics do much bette--quanttiatviely--at predicting quality trends in pretrained models%---quantitatively better at discriminating good-better-best, and qualitatively better at discriminating good-versus-bad models.
\item 
PL-based metrics can be used to characterize fine-scale model properties (including layer-wise \emph{Correlation Flow} and \emph{Scale Collapse} in poorly-trained models) and model enhancements (i.e. distillation, finetuning, etc.)
\end{itemize}

>>>>

To answer this question, we analyze hundreds of publicly-available pretrained state-of-the-art CV and NLP models. 
Here is a summary of our main results.
\begin{itemize}
\item
Norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models.
%, i.e., they can be used to discriminate between ``good-better-best'' models.
\item
However, norm-based meterics may fail for poorly-trained well-trained, i.e., to distinguish ``good-versus-bad''~models.
\item 
PL-based metrics do much better at predicting quality trends in CV/NLP models---quantitatively
%--at predicting quality trends in pretrained models%---quantitatively 
better at discriminating good-better-best, and qualitatively better at discriminating good-versus-bad models.
\item 
PL-based metrics can be used to characterize fine-scale model properties (including layer-wise \emph{Correlation Flow} and \emph{Scale Collapse} in poorly-trained models) and model enhancements (i.e. distillation, finetuning, etc.)
\end{itemize}
